Maximum Entropy Spectral Analysis: a case study

### 2021-03-05 paper/mesa.tex
another big chunk of edits

For this work, we are particularly interested in the mutli-dimensional case. Suppose we have a vector of measurements $(x(t_1),\ldots,x(t_n)) = (x_1, \ldots, x_n)$ that we conveniently express as a single realisation of an unknown stochastic process $x(t)$ and we have information about the expectation value of the process $\mu(t)$ and on the matrix of auto-covariances $C_{ij} \equiv C(t_i,t_j)$, then the MAXENT distribution is the $n$-dimensional multivariate Gaussian distribution\cite{gregory_2005}: 
\begin{align}
    p&\left((x_1, \ldots, x_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det C\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i,j}(x_i-\mu_i) (x_j-\mu_j)C^{-1}_{ij} \right)\,. 
\end{align}
We have already seen that for a wide-sense stationary process the mean function is independent of time, hence redefined to be equal to zero without loss of generality, and the auto-covariance function is dependent only on the time lag $\tau \equiv t_i - t_j$. One can thus choose a sampling rate $\Delta t$ so that $C_{ij} = C((i-j)\Delta t)$. The autocovariance matrix thus becomes a Toeplitz matrix. Toeplitz matrices are asymptotically equivalent to circulant matrices and thus diagonalised by the discrete Fourier transform base\cite{Gray}.
%R. M. Gray, Foundations and Trends⃝R in Communications and Information Theory 2, 155 (2005), URL https://doi.org/10.1561/0100000006.
Some simple algebra shows that the time-domain multivariate Gaussian can be transformed into the equivalent frequency domain 
probability distribution:
\begin{align}
p&\left((\tilde{x}_1, \ldots, \tilde{x}_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det S\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i}(\tilde{x}_i^2S^{-1}_{i} \right)\,,
\end{align}
where the matrix $S$ is an $n\times n$ diagonal matrix whose elements are the PSD $S(f)$ calculated at frequency $f_i$.
Many readers will recognised the familiar form of the Whittle likelihood that stands at the basis of the \emph{matched filter} method\cite{woodward}
%P. M. Woodward, D. W. Fry, and W. Higinbotham, Probability and information theory, with applications to radar; 2nd ed. (Pergamon Press, Oxford, 1964), URL http://cds.cern.ch/record/2031792.
and of gravitational waves data analysis, e.g. \cite{finn:1992}.
% L. S. Finn, Phys. Rev. D46, 5236 (1992), gr-qc/9209010
Thanks to MAXENT, the problem of defining the probability distribution describing a wide-sense stationary process is thus 
entirely reduced to the estimation of the PSD or, equivalently, the auto-covariance function.

@@

In a real implementation of the algorithm, computing all the recursion up to $M_{max}$ can result in a significant waste of computational power: the optimal value is often $m_{opt} << M_{max}$ and, in such cases, computing all the values of $m$ until $M_{max}$ is not useful.
In practice, we can apply an \textit{early stopping} procedure: every few iterations we look for the best order of $m_{opt}$; if this value does not change for a while, we assume that a good (local) minimum of the loss function is found and the computation is stopped.

@@

\subsection{Choosing a loss function - A gaussian PSD} \label{sec:arp_validation}
We test the performance of the three loss functions on a random time series generated with a known power spectral density.
We take the PSD to be a Gaussian distribution with mean $\mu = 2.5 \quad units$ and standard deviation $\sigma = 0.5 \quad units$, see Fig.~\ref{fig:autocorr}.
The time series will be generated by sampling a frequency vector from ${p(\tilde{n}(f_i)) \propto \exp{\left\{-\frac{1}{2}\sum_i\frac{n_i ^2}{S(f_i)}\right\}}}$, following the procedure outlined in ~\cite{}, and performing the inverse Fast Fourier Transform on the frequency series.

We will apply the Burg method choosing in turn each of the loss functions on an ensemble of simulated time series, 
thus obtaining an ensemble of PSD estimates, that will aloows the statistical characterisation of the performance of each loss function.
The disagreement between the PSD $S_i(f)$ estimated from the $i$-th simulated time series and the target PSD $S(f)$ is measured via 
the relative error $r_i$, averaged over all frequencies:
\begin{equation}\label{eq:freq_error}
r_i = \frac{1}{Ny}\sum_{f_j=0}^{f_j = Ny} \frac{|S_i(f_j) - S(f_j)|}{S(f_j)}
\end{equation}
where $Ny$ is the Nyquist frequency of the time series.

@@

For this investigation, we generate a dataset of 1000 time series of 3000 points each, see Fig.~\ref{fig:noise} for an example of a time series in frequency and time domain.
%In section~\ref{sec:LIGO_validation}, we will perform the analysis again using the Advanced LIGO design sensitivity PSD \cite{Ligo}.

@@

\paragraph{Final Prediction Error (FPE)}
The results of our investigation on the performance of FPE are reported in fig.~\ref{fig:FPEmean}.
Qualitatively, there is a good agreement between the reconstructed spectrum and the true spectrum; however, we note that the reconstruction is not very accurate in the low frequency region. 
Furthermore, the $90\%$ credible region is very small: this means that if we randomly take two of the reconstructed spectra, we expect their differences to be statistically small.
These facts are evidence for FPE to be a reliable loss function.

By looking at the red series in fig.~\ref{fig:optcomparison}, we note that the autoregressive orders obtained with FPE are clustered in a very small region. This is a desiderable property: FPE provides a stable estimation of the autoregressive order, which does not affect much the reconstruction error.
We conclude that the FPE shows good quality reconstruction for the spectrum and very desirable stability properties, its estimate for filter's length M is clustered in a region where there is no dependence of error from M. 
\paragraph{Optimum Bayes Decision Rule (OBD)}
The second loss function in consideration is OBD.
The results in fig.~\ref{fig:OBDmean} show a good agreement between the average over the reconstructions and the true spectrum.
Qualitatively the same behaviour of FPE is observed: a good quality reconstruction at the intermediate and high frequencies with a low $90\%$ confidence level; and a worse performance at low frequencies.
However, when looking at the error, the disagreement of this method is found to be larger than the one obtained with FPE: in the worst case, the error can gain a factor of $2$ as compared with FPE.

When plotting the error as a function of the autoregressive length (green series in fig.~\ref{fig:optcomparison}), the values taken by the OBD cluster in a small region, indicating the stability of the reconstructed process order $M$. We note that on average, OBD tends to choose smaller values of $M$ with respect to FPE: this can probably explain the observed large errors.

\paragraph{Criterion Autoregressive Transfer function (CAT)}
The performance of CAT are shown in fig.~\ref{fig:CATmean} and it is striking that CAT differs substantially from the other two loss functions considered.
The ensambled average PSD matches very well the ``true" PSD. This is also true even in the low frequency region, where the OBD and FPE had a poor performance.
However, the variance of the reconstructed spectrum is quite large (much larger than for FPE and OBD), and the relative error is quite high $~10\%$ and it approximately constant over all the frequencies.

The reason for this behaviour, can be found in fig.~\ref{fig:optcomparison} (black series). CAT does not converge to any specific value for the order of the autoregressive process.
In turn, the estimates for the order span a large range of values, hence the large variance observed.
Figure~\ref{fig:optcomparison} also shows a strong dependence of the error on the estimated length of the filter. The good quality of the reconstruction from the average spectrum can be explained as follows: long filters are able to capture features that short filters cannot see, like outliers in different realization of a noisy timeseries, but this is also responsible of an augmented variance in the estimate, by introducing spurious peaks in the reproduction.

When averaging the diffrerent PSD estimation, the noise in each spectrum cancels. It is interesting that the cancelling of errors in averaging is property of gaussian noise (the process is gaussian, after all). This implies, in a sense, that each estimate of the spectrum is independent of any other, as suggested by the huge variance in the residuals. This instability is not a good property for an estimation, so that this estimator might be found to be optimal for repeatable experiments and not for single observation of some process.

@@

In our analysis, FPE and OBD loss functions are found to behave similarly while CAT shows completely different properties.
CAT provides an accurate average spectrum over all the frequencies and large amount of variability; in turn OBD and FPE provide a poorer average in the low frequency tails with a lower variability (FPE with less noise than OBD).

The bad behavior in the reconstruction of the tails from OBD and FPE might be due to the fact that very small values require longer filters. 
In fact when we consider the average for all the spectra we note that short filters yield larger the error in the tails. OBD, which select the shortest filters, can provide an error as large as $300 \%$ at the extrema, as compared with $85\%$ error od FPE. In turn, CAT is $5\%$ accurate in those regions.

However, we see in figure \ref{fig:optcomparison} that a single PSD estimation with FPE is still able to provide the lowest averaged error over all frequencies, while CAT can reach error error $5$ times larger.
This is to say that CAT is the loss function that minimizes errors in the tails, FPE is found to reach best overall accuracy.

The conclusion is clear: even if in some cases CAT might be more accurate when taking the average over several estimation, FPE guarantees that the single estimation will be more accurate.
As in any common situation we cannot perform such averaging over different realization of the same time series, we must prefer FPE over CAT (let alone OBD, which even though qualitatively similar to FPE has worse performance).
However, if we indeed can measure the PSD by averaging over different time series, probably using CAT as a loss function is the best choice.
\sschmidt{This is similar to Welch: averaging over different time series to get a reliable result. Should we mention it?}
\sschmidt{C'erano ancora molti commenti: ho sintetizzato molto. Va bene? O si vuole aggiungere altro?}

@@

\subsection{Choosing a loss function - LIGO Spectrum} \label{sec:LIGO_validation}
In this subsection we concentrate again on the reconstruction of a specific, known, power spectrum: that is the Advanced LIGO design sensitivity theoretical spectral curve see fig.~\ref{fig:ligospectrum}.
For this analysis we will study properties on $500$ time series arrays of $40960$ points each. We set a sampling rate of $\SI{2048}{Hz}$ (this is $\SI{20}{s} of data$).
We chose a longer dataset to capture the complicated structure of the PSD. A shorter time batch would not have allowed us to reconstruct faithfully all the peaks of the empirical PSD.

\begin{figure}
    \centering
     \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates.pdf}
      \caption{Average spectrum for the three different loss function as compared with the ``true" PSD. The average is computed with $500$ realization of a $40960$ points long time series.}
       \label{fig:ligospectrum}
\end{figure}
In figure \ref{fig:ligospectrum}, we report the original spectrum and the ensemble averaged spectrum obtained with the three methods (no confidence level).
In figure \ref{fig:ligoPeaks} we plot a details od fig.~\ref{fig:ligospectrum} around the two peaks of the spectrum
In figure~\ref{fig:LigoOrderError}, we report, as above, a scatter plot with the frequency averaged error (eq.~\ref{eq:freq_error}) and the length of the autoregressive model obtained with each loss function.

The conclusions are very similar to those above. When averaged on multiple realization, CAT loss function is able to capture the spectrum very precisely.
In fact, even in presence of very sharp peaks, CAT reconstruction seems to be almost perfectly coincident with each of them (figs.\ref{fig:ligoPeaks}).
However, the computation on a single noise realization yields larger error, as manifest in fig.~\ref{fig:LigoOrderError}.
This supports the conclusion that CAT is not a stable optimizer: different computation of the same spectrum can output very different results.
On the other hand, FPE seems more robust and provides a smaller variance (and frequency averaged error), despite having a worse performance on the average.
We find again that FPE and OBD have similar performance: indeed, OBD shows qualitatively the same behaviour of FPE, although with slightly worse performance in the error.

We can then draw some general conclusions:
\begin{itemize}
	\item There are no reasons to prefer OBD over CAT or FPE.
	\item If we have one single realization for the process, we recommend the use of FPE, that would get the best resolution possible. In this situation, CAT would provide spurious and unreliable results, with large error.
	\item But, in case we have several realization for the same process, this last property of CAT, together with its instability, result to be his luck: averaging the spectrum over different time series tend to compensate noise in the results, originating a very well precise spectral estimation. The same is not true for FPE.
\end{itemize}

The choice of the loss function between CAT and FPE seems problem-dependent.

\begin{figure}[t]
        \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates_peaks.pdf}
        \caption{Details of peaks of the spectrum and their reconstruction with every optimizer}
        \label{fig:ligoPeaks}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/error_length_contour.pdf}
    \caption{For each of the $500$ independent realization of the time series, we plot the relative error $r$ (as in eq.~\ref{eq:freq_error}) against the length $m$ of autoregressive process. The time series are randomly drawn with a the analytical LIGO PSD in fig.`\ref{fig:ligospectrum}. Different colors refers to different choices for the loss function. Histograms for the distribution od the individual quantities are also represented.}
    \label{fig:LigoOrderError}
\end{figure}

>>>>

For this work, we are particularly interested in the mutli-dimensional case. Suppose we have a vector of measurements $(x(t_1),\ldots,x(t_n)) = (x_1, \ldots, x_n)$ that we conveniently express as a single realisation of an unknown stochastic process $x(t)$ and we have information about the expectation value of the process $\mu(t)$ and on the matrix of auto-covariances $C_{ij} \equiv C(t_i,t_j)$, then the MAXENT distribution is the $n$-dimensional multivariate Gaussian distribution\cite{gregory_2005}: 
\begin{align}
    p&\left((x_1, \ldots, x_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det C\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i,j}(x_i-\mu_i) (x_j-\mu_j)C^{-1}_{ij} \right)\,. 
\end{align}
We have already seen that for a wide-sense stationary process the mean function is independent of time, hence redefined to be equal to zero without loss of generality, and the auto-covariance function is dependent only on the time lag $\tau \equiv t_i - t_j$. One can thus choose a sampling rate $\Delta t$ so that $C_{ij} = C((i-j)\Delta t)$. The autocovariance matrix thus becomes a Toeplitz matrix. Toeplitz matrices are asymptotically equivalent to circulant matrices and thus diagonalised by the discrete Fourier transform base\cite{Gray}.
%R. M. Gray, Foundations and Trends⃝R in Communications and Information Theory 2, 155 (2005), URL https://doi.org/10.1561/0100000006.
Some simple algebra shows that the time-domain multivariate Gaussian can be transformed into the equivalent frequency domain 
probability distribution:
\begin{align}
p&\left((\tilde{x}_1, \ldots, \tilde{x}_n)\vert I\right) = \nonumber \\
    &\frac{1}{\left(2 \pi \det S\right)^{k / 2}}\exp\left(-\frac{1}{2}\sum_{i}\tilde{x}_i^2S^{-1}_{i} \right)\,,
\end{align}
where the matrix $S$ is an $n\times n$ diagonal matrix whose elements are the PSD $S(f)$ calculated at frequency $f_i$.
Many readers will recognise the familiar form of the Whittle likelihood that stands at the basis of the \emph{matched filter} method\cite{woodward}
%P. M. Woodward, D. W. Fry, and W. Higinbotham, Probability and information theory, with applications to radar; 2nd ed. (Pergamon Press, Oxford, 1964), URL http://cds.cern.ch/record/2031792.
and of gravitational waves data analysis, e.g. \cite{finn:1992}.
% L. S. Finn, Phys. Rev. D46, 5236 (1992), gr-qc/9209010
Thanks to MAXENT, the problem of defining the probability distribution describing a wide-sense stationary process is thus 
entirely reduced to the estimation of the PSD or, equivalently, the auto-covariance function.

@@

In a real implementation of the algorithm, computing all the recursion up to $M_{max}$ can result in a significant waste of computational power: the optimal value is often $m_{opt} << M_{max}$ and, in such cases, computing all the values of $m$ until $M_{max}$ is not useful.
In practice, we can apply an \textit{early stop} procedure: every few iterations we look for the best order of $m_{opt}$; if this value does not change for a while, we assume that a good (local) minimum of the loss function is found and the computation is stopped.

@@

\subsection{Choice of the loss function: Gaussian PSD} \label{sec:arp_validation}
We test the performance of the three loss functions on a random time series generated with a known power spectral density.
In this first experiment, we take the PSD to be a Gaussian distribution with mean $\mu = 2.5 \quad units$ and standard deviation $\sigma = 0.5 \quad units$, see Fig.~\ref{fig:autocorr}.
The time series are generated by sampling a frequency vector from ${p(\tilde{n}(f_i)) \propto \exp{\left\{-\frac{1}{2}\sum_i\frac{n_i ^2}{S(f_i)}\right\}}}$, following the procedure outlined in~\cite{}, and performing an inverse Fast Fourier Transform on the frequency series. 
For this investigation, we generate a dataset of 1000 time series of 3000 points each, see Fig.~\ref{fig:noise} for an example of a time series in frequency and time domain.

We then apply the Burg method choosing in turn each of the loss functions on an ensemble of simulated time series, 
thus obtaining an ensemble of PSD estimates, that will allows the statistical characterisation of the performance of each loss function.
The disagreement between the PSD $S_i(f)$ estimated from the $i$-th simulated time series and the target PSD $S(f)$ is measured via 
the relative error $r_i$, averaged over all frequencies:
\begin{equation}\label{eq:freq_error}
r_i = \frac{1}{Ny}\sum_{f_j=0}^{f_j = Ny} \frac{|S_i(f_j) - S(f_j)|}{S(f_j)}
\end{equation}
where $Ny$ is the Nyquist frequency of the time series.

@@

%In section~\ref{sec:LIGO_validation}, we will perform the analysis again using the Advanced LIGO design sensitivity PSD \cite{Ligo}.

@@

\paragraph{Final Prediction Error (FPE)}
The results of our investigation on the performance of FPE are shown in Fig.~\ref{fig:FPEmean}.
Qualitatively, there is a good agreement between the reconstructed spectrum and the true spectrum; 
however, we note that the reconstruction is not very accurate in the low frequency region. 
Furthermore, the $90\%$ credible region is very small: this means that if we randomly take two of the reconstructed spectra, we expect their differences to be statistically small. These facts are evidence for FPE to be a reliable loss function.

By looking at therRed series in Fig.~\ref{fig:optcomparison}, we note that the autoregressive orders obtained with FPE are clustered in a very small region. This is a desirable property: FPE, in fact, provides a stable estimation of the autoregressive order, which does not affect much the reconstruction error.
We conclude that the FPE shows good quality reconstruction for the spectrum and very desirable stability properties, its estimate for filter's length $m$ is clustered in a region where there is no dependence of error from $m$. 
\paragraph{Optimum Bayes Decision Rule (OBD)}
The second loss function in consideration is OBD. As for the FPE loss function, the results in Fig.~\ref{fig:OBDmean} show a 
good agreement between the average over the reconstructions and the true spectrum.
Qualitatively the same behaviour of FPE is observed: a good quality reconstruction at the intermediate and high frequencies with a low $90\%$ confidence level; and a worse performance at low frequencies.
However, when looking at the error, the disagreement of this method is found to be larger than the one obtained with FPE: in the worst case, the error can be as large as a factor of $2$ when compared with FPE.

The error as a function of the autoregressive length (green series in Fig.~\ref{fig:optcomparison}) cluster in a small region, indicating the stability of the reconstructed process order $m$. We note that on average, OBD tends to choose smaller values of $m$ with respect to FPE.

\paragraph{Criterion Autoregressive Transfer function (CAT)}
The performance of CAT is shown in Fig.~\ref{fig:CATmean}. At a first glance CAT differs substantially from the other two loss functions considered.
The ensemble-average PSD matches very well the underlying ``true" PSD. This is also true even in the low frequency region, 
where both OBD and FPE had a poor performance.
However, the variance of the reconstructed spectrum is quite large (much larger than for FPE and OBD), and the relative error is quite high, $\sim 10\%$ and it is approximately constant over all the frequencies.

The reason for this behaviour becomes clear from Fig.~\ref{fig:optcomparison} (black series). CAT does not converge 
to any specific value for the order of the autoregressive process.
In turn, the estimates for the order span a large range of values, hence the large variance observed.
Fig.~\ref{fig:optcomparison} also shows a strong dependence of the error on the estimated length of the filter. The good quality of the reconstruction from the average spectrum can be explained as follows: long filters are able to capture features that short filters cannot see, like outliers in different realization of the time-series, but this is also responsible of an increased variance in the estimate, by introducing spurious peaks in the reproduction.

When averaging the different PSD estimates, the noise in each spectrum cancels, as expected for Gaussian noise. 
This implies, in a sense, that each estimate of the spectrum is independent of any other, as suggested by the huge variance in the residuals. This lack of stability is not a good property for the estimation estimation of the PSD from a single realisation of the time-series, however, thanks to the averaging out of the errors, this estimator seems optimal in the case of repeatable experiments and ensemble-averages.

@@

In our analysis, the FPE and OBD loss functions are found to behave similarly while CAT shows fairly different properties.
CAT provides an accurate average spectrum over all the frequencies at the price of a large variance; in turn OBD and FPE 
provide a poorer average in the low frequency tails, however they also display a  smaller variance, with FPE showing the lowest.

The poor low-frequency reconstruction from OBD and FPE might be due to the fact that very small values require longer filters. 
In fact, when we consider the average for all the spectra we note that short filters yield larger the error in the tails. OBD, which select the shortest filters, can provide an error as large as $300 \%$ at the extrema, as compared with $85\%$ error of FPE. In turn, CAT is $5\%$ accurate in those regions.

However, we also note, see Fig.~\ref{fig:optcomparison}, that the psD inferred from a single time-series realisation with FPE is still able 
to provide the lowest averaged error over all frequencies, while CAT can reach errors $5$ times larger.
Hence, while CAT is the loss function that minimizes errors in the low-frequency end of the spectrum, 
FPE obtains the best overall accuracy.

The conclusion is clear: even if in some cases CAT might be more accurate when taking the average over several estimation, FPE guarantees that the single estimation will be more accurate.
As in any common situation we cannot perform such averaging over different realization of the same time series, we must prefer FPE over CAT (let alone OBD, which even though qualitatively similar to FPE has worse performance).
However, if we indeed can measure the PSD by averaging over different time series, using CAT as a loss function is the best choice. In this sense
we retain CAT to provide the best, and most similar in spirit, alternative to the commonly employed WelchPsd estimation method whenever 
ensemble-averages are needed and justified.

@@

\subsection{Choice of the loss function: LIGO Spectrum} \label{sec:LIGO_validation}
We continue our characterisation of the various loss functions considered in this work, by investigating the 
reconstruction of a specific, known, power spectrum: that is the Advanced LIGO design sensitivity theoretical spectral curve\wdp{add ref}.
For this analysis, we generate $500$ time series of $40960$ points each, sampled with a sampling rate of $\SI{2048}{Hz}$, hence we fix the duration
of the time-series to $\SI{20}{s}$. The chosen length is convenient to capture fairly accurately the low-frequency features of the LIGO PSD.

\begin{figure}
    \centering
     \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates.pdf}
      \caption{Average spectrum for the three different loss function as compared with the ``true" PSD. The average is computed with $500$ realization of a $40960$ points long time series.}
       \label{fig:ligospectrum}
\end{figure}
Our findings are summarised in Figs.~\ref{fig:ligospectrum} and ~\ref{fig:LigoOrderError}. The former shows the original spectrum (dashed line)
and the ensemble-averaged reconstructed PSD adopting the FPE (green line), OBD(red line) and CAT(black line). In all cases, the spectrum is well reconstructed, but with a fairly distinct behaviour at low frequency, where CAT -- as in the Gaussian case -- better captures and resolves the distinct 
spectral feature at $\sim 17$ Hz, see also the left panel in Fig.~\ref{fig:ligoPeaks}, as well as the high frequency line at $438$Hz, right panel in Fig.~\ref{fig:ligoPeaks}. 
Fig.~\ref{fig:LigoOrderError} shows the distribution of recovered AR orders $m$ against the relative frequency-averaged error. The behaviour
of the three loss functions is very similar to what found in the Gaussian PSD case: ODB infers the smallest orders and gives average errors around $20$\%, FPE consistently estimates orders of a few hundreds and shows the smallest errors $\sim 15$ \%while CAT does not show any preference towards any AR order and displays wildly varying errors. Yet again, when the PSD is averaged over multiple realization of the time, CAT is able to capture the spectrum very precisely. In fact, even in presence of very sharp peaks, CAT reconstruction seems to be almost perfectly coincident with each of them (figs.\ref{fig:ligoPeaks}).
Hence, also the study of simulated Advanced LIGO data seems to indicate that whenever and wherever ensemble-averaged PSD are necessary, CAT is the optimal choice of loss function. However, on a single time-series realisation, FPE is the more robust choice.

Let us summarise some key general conclusions:
\begin{itemize}
	\item There are no reasons to prefer OBD over CAT or FPE.
	\item If we have one single realization for the process, we recommend the use of FPE, that would get the best resolution possible. In this situation, CAT would provide spurious and unreliable results, with large error.
	\item In the case of several realizations of the same process, CAT ensemble-average properties provide very precise spectral estimation.\end{itemize}

Therefore, the choice of loss function, at least in between CAT and FPE, depends on the problem one  is attempting to solve.
\begin{figure}[t]
        \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/compare_estimates_peaks.pdf}
        \caption{Details of peaks of the spectrum and their reconstruction with every optimizer}
        \label{fig:ligoPeaks}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width = \linewidth]{Images/optimisers_comparison/ligo/error_length_contour.pdf}
    \caption{For each of the $500$ independent realization of the time series, we plot the relative error $r$ (as in eq.~\ref{eq:freq_error}) against the length $m$ of autoregressive process. The time series are randomly drawn with a the analytical LIGO PSD in fig.`\ref{fig:ligospectrum}. Different colors refers to different choices for the loss function. Histograms for the distribution od the individual quantities are also represented.}
    \label{fig:LigoOrderError}
\end{figure}
